---
title: "Untitled"
author: "Arturo"
date: "21/11/2017"
output: html_document
runtime: shiny
---



This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(readr)
library(dplyr)
library(lubridate)
library(tidyr)


base<-read_delim("/home/art/shiny-server/PVS/pruevashiny.csv", ";", escape_double = FALSE, locale = locale(date_names = "es", date_format = " %d/%m/%Y"), trim_ws = TRUE)
#base<-read_delim("/media/Datos/Data_science/Mis proyectos/shiny-server/PVS/pruevashiny.csv", ";", escape_double = FALSE, locale = locale(date_names = "es", date_format = " %d/%m/%Y"), trim_ws = TRUE)

base<-base[!is.na(base$Sexo),]
base$grupo <-ifelse(base$grupo=="Control","Control", "Intervención")

nm <- (as.Date("2016-05-01")%--%max(base$Fecha_Cita__yyyymmdd_))%/%months(1)

fechas <- as.Date("2016-05-01") + 0:nm * months(1)

source("/home/art/shiny-server/funciones.R")

```


```{r eruptions, echo=FALSE, fig.height=10, fig.width=10}

shinyApp( ui= fixedPage(
  column(6,inputPanel( h3("Filtrar:"),
  radioButtons("Sexo", "Sexo:", choices = list("Todos" = 1, "Hombres" = 2, "Mujeres" = 3), 
                   selected = 1),
  
  sliderInput("Edad", label = "Edad:",
              min = 10, max = 80, value = c(10,80))
     ),

inputPanel( h3("Estratificar por:"),
       radioButtons("Estra", "Estratos:", choices = list("Ninguno" = 1, "Sexo" = 2, "Edad" = 3), 
                   selected = 1))
  ),
column(1),
column(5, inputPanel( h3("Analizar:"),
   checkboxGroupInput("Habitos", label = h4("Hábitos"), 
    choices = list("A1 (al menos un hábito)" = "A1", "A1 Actividad física" = "A1_AF", "A1 Dieta" = "A1_DT", 
                   "A1 Tabaco" = "A1_TB")))),       


plotOutput("grafiPlot", height=470)
),

server = function(input, output) {

output$grafiPlot <- renderPlot({
  
  bas<-filter(base, edad_consult>input$Edad[1], edad_consult<(input$Edad[2]+1))
  
  if (input$Sexo == 2)  bas <- bas %>% filter(Sexo == "Hombre")
  if (input$Sexo == 3)  bas <- bas %>% filter(Sexo == "Mujer")
  
  if (input$Estra == 1) bas <- bas %>% curva_pro() %>% gather(habito, porcen, -fechas)
  if (input$Estra == 2) bas <- bas %>% split(bas$Sexo) %>% lapply(curva_pro) %>% bind_rows(.id="Sexo") %>%  
    gather(habito,porcen, -c(fechas, Sexo))
  if (input$Estra == 3) bas <- bas %>% split(bas$edad) %>% lapply(curva_pro) %>% bind_rows(.id="Edad") %>% gather(habito, porcen, -c(fechas, Edad))
  
  bas <- bas %>%  filter(habito %in% input$Habitos)
  
  p <- ggplot(bas, aes(x=fechas, y = porcen, col = habito)) + geom_line()
  if (input$Estra == 2) p <- p + facet_wrap(~Sexo)
  if (input$Estra == 3) p <- p + facet_wrap(~Edad)
  
  print(p)
  
})
}  
)
```

cxcczxcx<zcxzcx<czxccddsac

fdsfsdafdasfasdfasdf

##otrasd  cosas
dsfdsafdasfasdf
dfsdafasdfasdfsdafasdfdsaf
dfdsfdsafasdfadsf
fdsfsdafasdfdsafdsafdasfdsafsdafs    

dsfsdsf 

# dsfsdafdas sdfsdaf sdfsd
cxz  xc<czx
sdadsa

dfsdfasd

